Edge effects and optimal field sizes in Alberta

### 2021-06-22 Manuscript/manuscript.Rmd
Worked on manuscript and started TMB tests

- Yield data was collected in rectangles of the same length as the data interval (distance = speed $\times$ interval, typically 1 second) and the same width as the combine header (5-7 m)
  - We extracted the size of each polygon (m$^2$), dry yield (tonnes), and the spatial location, and the sequence of collection (1 - end of harvest)
  - Because of the large number of yield rectangles per field (30-800 thousand), we used the centroid of each polygon as its location, treating areal data as point data
  - Seeding and application rates were constant across fields, so we did not consider inputs in our analysis
  - We used dry yield (tonnes of seed/hectare after accounting for crop moisture) as our measure of crop yield
  - Due to the high number of samples at each field, we sub-sampled to 50,000 data points per field to reduce computation time

>>>>

- Yield data is collected in rectangles of the same length as the data interval (distance = combine ground speed $\times$ interval, typically 1 second) and the same width as the combine header (5-7 m)
  - We extracted the size of each polygon (m$^2$), dry yield (tonnes), and the spatial location, and the sequence of collection (1 - end of harvest)
  - Because of the large number of yield rectangles per field (30-800 thousand), we used the centroid of each polygon as its location, treating areal data as point data
  - Seeding and application rates were constant across fields, so we did not consider inputs in our analysis
  - We used dry yield (tonnes of seed/hectare after accounting for crop moisture) as our measure of crop yield
  - Due to the large number of data at each field, we sub-sampled to 50,000 data points per field to reduce computation time
